### 2024-10-23 acronyms/acronyms.tex
ipcc
wef
bea
ians acronyms
acronyms
neup
bpc acronyms

>>>>

\newacronym{ipc}{IPCC}{Intergovernmental Panel on Climate Change}
\newacronym{wef}{WEF}{World Economic Forum}
\newacronym{bea}{BEA}{Battelle Energy Alliance}
\newacronym{cd}{CD}{Certificate of Deposit}
\newacronym{bn}{BN}{Bayesian Network}
\newacronym{ann}{ANN}{Artificial Neural Network}
\newacronym{gsa}{GSA}{General Services Administration}
\newacronym{gra}{GRA}{Graduate Research Assistant}
\newacronym{fna}{F\&A}{Facilities and Administrative}
\newacronym{mdc}{MTDC}{Modified Total Direct Cost}
\newacronym{nce}{NCES}{National Center for Education Statistics}
\newacronym{sde}{SDE}{Idaho State Department of Education}
\newacronym{usd}{USDA}{United States Department of Agriculture}
\newacronym{hrc}{HERC}{Higher Education Research Council}
\newacronym{igm}{IGEM}{Idaho Global Entrepreneurial Mission Initiative}
\newacronym{rad}{RADICL}{Reconfigurable Attack-Defend Instructional Computing Laboratory}
\newacronym{lea}{LEA}{Local Educational Agency}
\newacronym{ida}{IDAPA}{Idaho Administrative Procedures Act}
\newacronym{iee}{IEEE}{Institute of Electrical and Electronics Engineers}
\newacronym{cis}{CISSE}{Colloquium for Information Systems Security Education}
\newacronym{ngo}{NGO}{Non-Governmental Organization}
\newacronym{vo}{CPS-VO}{CPS Virtual Organization}
\newacronym{nkn}{NKN}{Northwest Knowledge Network}
